\chapter{Introduction} 

\clearpage
\section{Overview}

There has been a rise in online meetings because of work from home culture. There are employees from different countries who are not always comfortable with English, therefore company’s translator easily translates the language into comfortable languages. There are several languages across the world and each language is different from others in one sense or the other. Like English, Hindi, Spanish, French, Russian, Japanese, Korean, etc. Also, the company’s data is confidential so the translator should be of the company’s trust, otherwise, companies can suffer because of data loss.
To resolve this issue translator was introduced using machine learning techniques. There are various AI-based translators like Google Translate, Microsoft Translate, Amazon Translate, and many more. 
 \newpage

\section{Motivation} 
Recently online meetings have taken a rise, but during the meetings, if there are people from many countries then it is very hard to explain everyone everything in their native language. So, to improve the functionalities Translation as a Service model is used by which the user input is taken as voice it is converted to text. After that text is converted into the required language after that we convert the text to voice which the people can hear the translated language output which will help them understand what the presenter wants to present. The input will be taken from the inbuilt microphone and the output will be given back from the speaker.
\\
\section{Problem Statement}
To build a deep learning model using Neural Machine Translation which can convert one language speech to required language and will give output in form of speech which will be useful in meetings 

\newpage

\section{Objectives}
The project is aimed to design a deep-learning model with the following features
\begin{enumerate}
    \item Capturing the Speech
    \item Importing pre-trained model
    \item Converting Speech to Text
    \item Translating text to required language
    \item Converting text to Speech 
\end{enumerate}

\newpage

\section{Project Planning}
\begin{table}[htbp]
   
\begin{tabular}{|c|>{\centering\arraybackslash} p{5cm}|c|c|}
    \hline
    Sr. No. & Activity & Start Date & End Date \\
    \hline
    \hline
    1 & Topic selection: TaaS & 5 August 2022 & 8 August 2022 \\
    \hline
    2 & Feasibility study and research & 5 August 2022 & 16 August 2022 \\
    \hline
    3 & Research paper summary & 12 August 2022 & Ongoing \\
    \hline
    4 & Designing of the system architecture, and approval of topic & 16 August 2022 & 20 August 2022\\
    \hline
    5 & Workbook printout & 20 August 2022 & 20 August 2022 \\
    \hline
    6 & Project Review 1: Presentation of the system architecture model, and further approach on topic & 3 September 2022 & 3 September 2022 \\
    \hline
    7 & Further research on the topic of speech to text and text to speech translation & 4th Septmber 2022 & Ongoing \\
    \hline
    8 & Software design planning & 4th September 2022 & 10 September 2022 \\
    \hline
    9 & Development of the translator model using NMT Neural machine translator (Basic model) &15th September 2022 & Ongoing \\
    \hline
    & Project Review II & 21 November 2022 & 21 November 2022 \\
    \hline
    
\end{tabular}
    \caption{Project Planning}
    \label{tab:my_label}
\end{table}